Structural Divergence Analysis

### 2017-06-04 analysis-structure-CN-WCN.Rmd
estructura-CN/WCN

# compare profiles

CA.cor.p = c()
CA.cor.s = c()

@@

plot(x = d.exp$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

plot(x = d.exp$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

# WCN
plot(x = d.exp$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

@@

# compare profiles

CM.cor.p = c()
CM.cor.s = c()

@@

plot(x = d.exp$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

plot(x = d.exp$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.5.CM), xlab = "<zRSDi> experimental")

>>>>

# compare profiles
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

@@

plot(x = d.exp$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

######
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

#######
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

#####
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.5.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.5.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.5.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.5.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

#####
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.6.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.6.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.6.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.6.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

#####
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.7.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.7.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.7.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.7.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

# WCN
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN.CA))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN.CA))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN.CA), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN.CA), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")

@@

# compare profiles
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CM))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CM))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CM), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CM), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

@@

plot(x = d.exp$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CM))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CM))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CM), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CM), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

######
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CM))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CM))

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM), method = "spearman")
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CM), method = "spearman")
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CM), method = "spearman")

cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")

#######
## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> experimental")
plot(x = d.mut$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> no-selection")
plot(x = d.medium$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM))
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CM))
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CM))
